\vspace{-5mm} \fontsize{24pt}{12pt}\selectfont \textbf{What's So Special About Philosophy?}

### 2015-10-17 writeup/draft.tex
created traversal figures

While some libraries exist for MediaWiki Markup, we opted to develop our own algorithm for parsing the first link in the XML version of each article.\footnote{
Approaches using existing libraries led to several bugs 
including trouble with nested links, nested parenthesis, unclosed tags, escape characters 
as well as compatibility with other libraries used to parse the XML.}
Our parsing algorithm aimed to: 
1. squash the initial bugs 
2. eliminate the need for several passes. 
To process an article with one pass, we developed a hierarchical system of flags:
\begin{itemize}
    \item[Flag 1:] inside template?
    \begin{itemize}
        \item[Flag 2:] inside <ref>, <div>?
        \begin{itemize}
            \item[Flag 3:] inside ()?
        \end{itemize}
    \end{itemize}
\end{itemize}

@@

\begin{figure}[H]
\centering
    \caption{distribution of traversal visits}
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{graphics/top_1k_100_pages.png}
    \end{subfigure}
\end{figure}

\red{[[change title from "pages" to "articles" for consistency]]} \\
\red{[[justify scale-free with log-log or power measure]]} \\

@@

\begin{figure}[H]
\centering
    \caption{highest ranking articles by number of traversals}
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth, angle=-90]{graphics/top_articles_list.png}
    \end{subfigure}
\end{figure}

@@

\subsubsection{Measure Number of Synonyms}
\red{
[[ add synonym analysis to support characterization of high ranking articles
as abstract foundational notions. \\
- idea is to correlate the number of synonyms a word has with its traversal visit rank.
]]}

>>>>

While some libraries exist for MediaWiki Markup, we opted to develop our own algorithm for parsing the first link in the XML version of each article.\footnote{
Approaches using existing libraries led to several bugs 
including trouble with nested links, nested parenthesis, unclosed tags, escape characters 
as well as compatibility with other libraries used to parse the XML.}
Our parsing algorithm aimed to: 
1. squash the initial bugs 
2. eliminate the need for several passes. 
To process an article with one pass, we developed a hierarchical system of flags:
\begin{itemize}
    \item[Flag 1:] inside Wikimedia template?\\
        * \bt{trigger}: \{\{
    \begin{itemize}
        \item[Flag 2:] inside <ref>, <div>?
        \begin{itemize}
            \item[Flag 3:] inside ()?
        \end{itemize}
    \end{itemize}
\end{itemize}

@@

\begin{figure}[H]
\centering
    \caption{distribution of traversal visits}
        \includegraphics[width=\textwidth]{graphics/traversals_per_article.png}
\end{figure}

distribution of visits blah blah
\begin{figure}[H]
\centering
\caption{traversal visit distribution of highest ranking articles}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{graphics/top_1k_article_traversals.png}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{graphics/top_100_article_traversals.png}
\end{subfigure}
\end{figure}

@@

\begin{figure}[H]
\centering
    \caption{highest ranking articles by number of traversals}
        \includegraphics[width=0.6\textwidth]{graphics/articles_ranked.png}
\end{figure}

@@

\subsubsection{Measure Number of Synonyms}

\green{
number of synonyms
top 100 articles, average:
5.0 
9.1 (excluding zero)
median: 7.0

remaining articles average:
0.5
5.8 (excluding zero)
median: 3.0
}
\red{
[[ add synonym analysis to support characterization of high ranking articles
as abstract foundational notions. \\
- idea is to correlate the number of synonyms a word has with its traversal visit rank.
]]}
